Contract Modules

### 2020-11-25 papers/contract-modules/modules.tex
update
syntax

\begin{lstlisting}[language=caml]
contract module MyContract = "kt1..."
  entry point bid_for_auction Left (_ : int) 
  raises "closed" as closed       (* auction closed*)
         "bid too low" as too_low (* bid received is too low *)
         42 as the_answer         (* failwith received argument 42 *)
         (_ : int) as failedwith  (* failwith received an integer arg *)

  entry point close_auction Right (_ : unit)
  raises "not owner"         (* caller cannot close the auction *)
\end{lstlisting}

@@

\begin{lstlisting}[language=caml]
signature MyContract =
sig 
  type bid_for_auction_errors = 
     | closed 
     | too_low 
     | the_answer
     | failedwith of int

@@

>>>>

Suppose the parameter type of a smart contract is defined by this Michelson code:
\begin{verbatim}
parameter union (int %bid_for_auction) (unit %close_auction)
...
\end{verbatim}

\begin{lstlisting}[language=caml]
contract type MyContract = sig
  entrypoint %bid_for_auction (_ : int) 
  raises "closed" as closed       (* auction closed*)
       | "bid too low" as too_low (* bid received is too low *)
       | 42 as the_answer         (* failwith received argument 42 *)
       | (_ : int) as failedwith  (* failwith received an integer arg *)

  entrypoint %close_auction (_ : unit)
  raises "not owner"         (* caller cannot close the auction *)
end
\end{lstlisting}

@@

\begin{lstlisting}[language=caml]
module type MyContract =
sig 
  type bid_for_auction_errors = 
     | closed 
     | too_low 
     | the_answer
     | failedwith of int

@@

A starting point for the implementation could be the module \lstinline/Tezos_micheline/, which has a
Michelson parser.
